Fast and Flexible Dynamic Binary Translation for the Kernel

### 2013-12-19 VEE-14/paper.tex
Some minor updates to the RCU section.

\toolname{RCUdbg} gains visibility on RCU operations in two ways: \begin{enumerate}
	\item The Linux kernel RCU implementation is annotated to provide more information to \toolname{RCUdbg}. This information includes source code file and line information for bug reporting, and additional memory references that \toolname{RCUdbg} uses to get better visibility on bugs. These annotations are strictly internal to the RCU API, and thus require no changes to code using this API.
	\item The annotated RCU API functions are specialized using Granary's function wrapping feature (\Cref{sec:function_wrapper}). Specifically, 
\end{enumerate}

@@

>>>>

\toolname{RCUdbg} gains visibility on RCU operations in three ways: \begin{enumerate}
	\item The Linux kernel RCU implementation is annotated to provide more information to \toolname{RCUdbg}. This information includes source code file and line information for bug reporting, and additional memory references that \toolname{RCUdbg} uses to get better visibility on bugs. These annotations are strictly internal to the RCU API, and thus require no changes to code using this API.
	\item The annotated RCU API functions are specialized using Granary's function wrapping feature (\Cref{sec:function_wrapper}). Interposing on these functions allows \toolname{RCUdbg} to add an address watchpoint to the address returned by \texttt{rcu\_\linebreak[0]dereference}, and to correlate uses of \texttt{rcu\_\linebreak[0]dereference} and \texttt{rcu\_\linebreak[0]assign\_\linebreak[0]pointer}.
	\item Read-side critical sections are discovered at instrumentation time (rather than run time) by observing \texttt{call}s to \texttt{rcu\_\linebreak[0]read\_\linebreak[0]lock} and \texttt{rcu\_\linebreak[0]read\_\linebreak[0]unlock}, respectively. This allows \toolname{RCUdbg} to instrument code running inside of read-side critical sections using one policy ($P_{read}$), and code running outside of read-side critical sections using another policy ($P_{outside}$).
\end{enumerate}

@@

Perhaps I should do one...
